Why aren't significance tests commonly used for linear regression diagnostics?

### 2022-12-13 paper_comparison/paper_comparison/paper_comparison.Rmd
use a different residual plot in VI example

```{r first-example-lineup, fig.cap="Visual testing is conducted using a lineup, as in the example here. The residual plot computed from the observed data (plot 7, exhibiting non-linearity) is embedded among 19 null plots, where the residuals were simulated from a standard error model. Computing the $p$-value requires that the lineup be examined by a number of human judges, each asked to select the most different plot. A small $p$-value would result from a substantial number selecting plot 7."}

@@

vi_lineup$poly_422$data %>%
  VI_MODEL$plot_lineup(theme = theme_light(), remove_axis = TRUE, remove_grid_line = TRUE)
```

Figure \ref{fig:first-example-lineup} is an example of a lineup protocol. If the actual data plot at position 7 is identifiable, then it is evidence for the rejection of $H_0$ that the regression model is correctly specified. In fact, the actual residual plot is obtained from a misspecified regression model with non-linearity issue.

The effectiveness of lineup protocol is validated by @majumder_validation_2013 under relatively simple classical normal linear regression model settings with one or two regressors. Their results suggest visual test is capable of testing the significance of a single regressor with a similar power as a t-test, though they expressed that in general it is unnecessary to use visual inference if there exists a conventional test and they didn't expect the visual test to perform equally well as the conventional test. In their third experiment, where there does not exist a proper conventional test, visual test outperforms the conventional test for a large margin. This is encouraging as it promotes the use of visual inference in border field of data science where there are no existing statistical testing procedures. Visual inference have also been integrated into diagnostic of hierarchical linear models by @loy2013diagnostic, @loy2014hlmdiag and @loy2015you. They use lineup protocols to judge the assumption of linearity, normality and constant error variance for both the level-1 and level-2 residuals.

>>>>

```{r first-example-lineup, fig.cap="Visual testing is conducted using a lineup, as in the example here. The residual plot computed from the observed data (plot $2^2 + 2$, exhibiting non-linearity) is embedded among 19 null plots, where the residuals were simulated from a standard error model. Computing the $p$-value requires that the lineup be examined by a number of human judges, each asked to select the most different plot. A small $p$-value would result from a substantial number selecting plot $2^2 + 2$."}

@@

# vi_survey %>%
#   filter(!attention_check) %>%
#   filter(!null_lineup) %>%
#   filter(type == "polynomial") %>%
#   filter(x_dist == "uniform") %>%
#   filter(n == 300) %>%
#   filter(shape == 1) %>%
#   group_by(unique_lineup_id) %>%
#   summarise(effect_size = first(effect_size)) %>%
#   arrange(effect_size)

vi_lineup$poly_300$data %>%
  VI_MODEL$plot_lineup(theme = theme_light(), remove_axis = TRUE, remove_grid_line = TRUE)
```

Figure \ref{fig:first-example-lineup} is an example of a lineup protocol. If the actual data plot at position $2^2 + 2$ is identifiable, then it is evidence for the rejection of $H_0$ that the regression model is correctly specified. In fact, the actual residual plot is obtained from a misspecified regression model with non-linearity defect.

The effectiveness of lineup protocol is validated by @majumder_validation_2013 under relatively simple classical normal linear regression model settings with one or two regressors. Their results suggest that visual test is capable of testing the significance of a single regressor with a similar power as a t-test, though they express that in general it is unnecessary to use visual inference if there exists a conventional test and they do not expect the visual test to perform equally well as the conventional test. In their third experiment, where there does not exist a proper conventional test, visual test outperforms the conventional test for a large margin. This is encouraging as it promotes the use of visual inference in border field of data science where there are no existing statistical testing procedures. Visual inference have also already been integrated into diagnostic of hierarchical linear models by @loy2013diagnostic, @loy2014hlmdiag and @loy2015you. They use lineup protocols to judge the assumption of linearity, normality and constant error variance for both the level-1 and level-2 residuals.

### 2022-12-13 paper_comparison/paper_comparison/paper_comparison.tex
use a different residual plot in VI example

\caption{Visual testing is conducted using a lineup, as in the example here. The residual plot computed from the observed data (plot 7, exhibiting non-linearity) is embedded among 19 null plots, where the residuals were simulated from a standard error model. Computing the $p$-value requires that the lineup be examined by a number of human judges, each asked to select the most different plot. A small $p$-value would result from a substantial number selecting plot 7.}\label{fig:first-example-lineup}
\end{figure}

Figure \ref{fig:first-example-lineup} is an example of a lineup
protocol. If the actual data plot at position 7 is identifiable, then it
is evidence for the rejection of \(H_0\) that the regression model is
correctly specified. In fact, the actual residual plot is obtained from
a misspecified regression model with non-linearity issue.

The effectiveness of lineup protocol is validated by
\citet{majumder_validation_2013} under relatively simple classical
normal linear regression model settings with one or two regressors.
Their results suggest visual test is capable of testing the significance
of a single regressor with a similar power as a t-test, though they
expressed that in general it is unnecessary to use visual inference if
there exists a conventional test and they didn't expect the visual test
to perform equally well as the conventional test. In their third
experiment, where there does not exist a proper conventional test,
visual test outperforms the conventional test for a large margin. This
is encouraging as it promotes the use of visual inference in border
field of data science where there are no existing statistical testing
procedures. Visual inference have also been integrated into diagnostic
of hierarchical linear models by \citet{loy2013diagnostic},
\citet{loy2014hlmdiag} and \citet{loy2015you}. They use lineup protocols
to judge the assumption of linearity, normality and constant error
variance for both the level-1 and level-2 residuals.

>>>>

\caption{Visual testing is conducted using a lineup, as in the example here. The residual plot computed from the observed data (plot $2^2 + 2$, exhibiting non-linearity) is embedded among 19 null plots, where the residuals were simulated from a standard error model. Computing the $p$-value requires that the lineup be examined by a number of human judges, each asked to select the most different plot. A small $p$-value would result from a substantial number selecting plot $2^2 + 2$.}\label{fig:first-example-lineup}
\end{figure}

Figure \ref{fig:first-example-lineup} is an example of a lineup
protocol. If the actual data plot at position \(2^2 + 2\) is
identifiable, then it is evidence for the rejection of \(H_0\) that the
regression model is correctly specified. In fact, the actual residual
plot is obtained from a misspecified regression model with non-linearity
defect.

The effectiveness of lineup protocol is validated by
\citet{majumder_validation_2013} under relatively simple classical
normal linear regression model settings with one or two regressors.
Their results suggest that visual test is capable of testing the
significance of a single regressor with a similar power as a t-test,
though they express that in general it is unnecessary to use visual
inference if there exists a conventional test and they do not expect the
visual test to perform equally well as the conventional test. In their
third experiment, where there does not exist a proper conventional test,
visual test outperforms the conventional test for a large margin. This
is encouraging as it promotes the use of visual inference in border
field of data science where there are no existing statistical testing
procedures. Visual inference have also already been integrated into
diagnostic of hierarchical linear models by \citet{loy2013diagnostic},
\citet{loy2014hlmdiag} and \citet{loy2015you}. They use lineup protocols
to judge the assumption of linearity, normality and constant error
variance for both the level-1 and level-2 residuals.
